Notes on @nolan2010computing

### 2019-11-08 Rmd/methods.Rmd
updated methods text

Our computational system for acquiring tweets involved several steps. We interacted with the API via the R package `twitteR` [@twitteR]. We used the free Twitter streaming API that gave us access to approximately one percent stream of all tweets during the specified query time period. To ensure that we collected tweets continuously, we used the linux tool `crontab` to execute our R script every five minutes. Each execution of the R script performed a single streaming API query, lasting five minutes. Twitter's streaming API, at the time of our data collection, enforced rate limits on the frequency and duration of queries.

@@

Our framework, and the projects developed under it, encourage students to deepen 
computational reasoning skills in several ways. First, they work with a variety of 
internet-based data to answer research questions. In the two example cases, our 
students collected tweets over time and gathered complementary data from other 
resources, including daily closing prices of stock market indexes.

Second, the students worked with a variety of data structures. 
The Twitter streaming 
API returns tweets as JSON files. Because distinct Twitter users may provide 
different pieces of profile information, there is variability in the structure of 
each tweet's JSON entry. Students needed to recognize this, and write code that 
accommodated these variations in tweet data structure.

@@

>>>>

Our computational system for acquiring tweets involved several steps. We interacted 
with the API via the R package `twitteR` [@twitteR]. We used the free Twitter streaming 
API that gave us access to approximately one percent stream of all tweets during the 
specified query time period. To ensure that we collected tweets continuously, we used 
the linux tool `crontab` to execute our R script every five minutes. Each execution of 
the R script performed a single streaming API query, lasting five minutes. Twitter's 
streaming API, at the time of our data collection, enforced rate limits on the 
frequency and duration of queries. With the above settings, we continuously collected 
tweets.

@@

Our framework, and the projects developed under it, encourage students to deepen 
computational reasoning skills in several ways. First, they work with a variety of 
internet-based data to answer research questions. In the two example cases, our 
students collected tweets over time and gathered complementary data from other 
resources, including daily closing prices of stock market indexes. This gave students 
opportunities to think creatively about what data to acquire and how to use multiple 
data sources in a single cohesive project.

Second, the students worked with a variety of data structures. 
The Twitter streaming 
API returns tweets as JSON (Javascript Object Notation, http://json.org). Because 
distinct Twitter users may provide 
different pieces of profile information, there is variability in the structure of 
each tweet's JSON. Additionally, tweet metadata fields may appear in any order (https://developer.twitter.com/en/docs/tutorials/consuming-streaming-data). 
Students needed to recognize this and write code that 
accommodated these variations in tweet data structure.

Students wrote code to parse and organize tweet JSONs. Each tweet's JSON included required fields, and, possibly, some optional fields. The required fields are:

**see https://developer.twitter.com/en/docs/tweets/data-dictionary/overview/tweet-object**

The evolving nature of JSON tweet structure 
(https://developer.twitter.com/en/docs/tweets/data-dictionary/guides/tweet-timeline) 
required students to write flexible code that could incorporate newly introduced 
or deprecated metadata.

@@

computational topics: LDA & topic modeling; time series analysis; sentiment analysis.

data analysis and practice of statistics:
